Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-19 main.Rmd
hierarchy table and order re-write

In \autoref{sec:cyclic-gran}, we discussed how we can define cyclic granularities by extending the framework of linear granularities defined in @Bettini1998-ed. In this section, we will see how to obtain cyclic granularities through an algebraic representation of other cyclic granularities <!--This is similar to calendar algebra in @Ning2002-tf, where linear granularities are generated from the bottom linear granularity or from those that are already generated. Since, our method caters to computation of cyclic granularities, we shall refer to it as--> through cyclic calendar algebra operations.

@@

**Hierarchy table** Let $H_n: (G, C, P)$ be a hierarchy table containing $n$ linear granularities. $G_{l}$ represents the linear granularity of order l and $P(l,m)$ represents the period length of $G_{l}$ with respect to $G_{m}$ and $C_{G(l),G(m)}$ represents the cyclic granularity that relates linear granularity of order l and m, $\forall l,m \in {1, 2, \dots,n}$ and $l<m$.

**Order** of a linear granularity can be comprehended as the level of graininess associated with a linear granularity. For example, if we consider two linear granularities $G$ and $H$, such that $G$ is finer than or groups into $H$, then $H$ is of higher order than $G$. In any hierarchy table, linear granularities are arranged from lowest to highest order of linear granularities.

We refer to granularities which are nested within multiple levels of the hierarchy table as _multiple-order-up_ granularities and those concerning a single level as _single-order-up_ granularities.

>>>>

In Section \ref{sec:cyclic-gran}, we discussed how we can define cyclic granularities by extending the framework of linear granularities defined in @Bettini1998-ed. In this section, we will see how to obtain cyclic granularities through an algebraic representation of other cyclic granularities <!--This is similar to calendar algebra in @Ning2002-tf, where linear granularities are generated from the bottom linear granularity or from those that are already generated. Since, our method caters to computation of cyclic granularities, we shall refer to it as--> through cyclic calendar algebra operations.

@@

**Order** of a linear granularity can be comprehended as the level of coarseness associated with a linear granularity. For two linear granularities $G$ and $H$, if $G$ groups into $H$ or $H$ is composed of higher number of granules of the bottom granularity than $G$, then $G$ is of lower order than $H$. In any hierarchy table, linear granularities are arranged from lowest to highest order.

**Hierarchy table** Let $H_n: (G, C, K)$ be a hierarchy table containing $n$ linear granularities. $G_{l}$ and $G_{m}$ represent the linear granularity of order $l$ and $m$ respectively with $l<m$. $K \equiv P(l,m)$ represents the period length of $G_{l}$ with respect to $G_{m}$ for circular granularity $C_{G(l),G(m)}$ and $K \equiv k(l,m)$ represents the operation to obtain $G_{m}$ from $G_{l}$ for quasi-circular granularity $C_{G(l),G(m)}$, $\forall l,m \in {1, 2, \dots,n}$. We assume that the cyclic granularity $C_{G(l),G(m)}$ is either circular or quasi-circular. It is difficult to position an aperiodic linear granularity in a hierarchy and hence the possibility of an aperiodic cyclic granularity is not considered.

We refer to granularities which are nested within multiple levels of the hierarchy table as _multiple-order-up_ and those concerning a single level as _single-order-up_ granularities.
